### 2016-09-12 precip/doc/precip_experiment_ms.Rmd
moving all my files to a new directory within the main project directory. This will facilitate organized merging with Peters directory

\textsc{\small{Andrew R. Kleinhesselink\footnote{Corresponding author: arklein@aggiemail.usu.edu}\textsuperscript{1}, Peter B. Adler\textsuperscript{1} and Andrew Tredennick\textsuperscript{1}}}

@@

Materials and Methods
---------------------
#### Multi-year plant community data  
Long-term data on individual abundance and size of plants in a sagebrush steppe community have been collecting since the 1930s at the US Sheep Experiment Station in Dubois Idaho.  The plots were recensused beginning in 2007 using methods identical to the original studies. These data allow for the fitting of statistical models that estimate the effects of climate and competitive effects on individual plants in the plots.  In theory these statistical models can be used to project the effects of both a change in the competitive environment at this site--or a change in the climate.

@@

### Estimating climate effects on vital rates

@@

>>>>

\textsc{\small{Andrew R. Kleinhesselink\footnote{Corresponding author: arklein@aggiemail.usu.edu}\textsuperscript{1}, Peter B. Adler\textsuperscript{1}, Andrew Tredennick\textsuperscript{1}, Caitlin Andrews{2}\textsuperscript{2} and John Bradford\textsuperscript{2} }

@@

Materials and Methods
---------------------
#### Multi-year plant community data  
Long-term data on individual abundance and size of plants come from the US Sheep Experiment Station (USSES) in Dubois, Idaho, USA (44\degree 12' N, 112\degree 1' W, 1500 m A.S.L.). This recieves 307 mm of precipitation annually and has a mean annual temperature of 6.2\degree C.  The vegetation is dominated by three perennial grasses, Pseudoroegneria spicata (Syn. Pascopyrum spicata), Poa secunda (Syn. Poa sandbergii), and Hesperostipa comata (Syn. Stipa comata), and one small woody shrub, Artemisia tripartita [Asteraceae].

Our historical data come from permanent plot monitoring at the USSES conducted annually from 1923 to 1957.  The permanent plots are 1 x 1 m and the corners were marked with steel bars so that they could be precisely relocated year after year. The size and position of each individual plant within the plots was recorded on paper maps using a mechanical tracing device called a pantograph.  This method accurately reproduces the exact spatial configuration of plants within a plot in a given year to less than 1 cm accuracy.

Beginning in 2007, 18 of the original permanent plots were relocated and re-measured annually using the same methods as the original investigators. The permanent plots measured in this contemporary period were located within three areas that had been ungrazed since the 1920's.

@@

### Estimating effects of climate and competition on vital rates

We fit our predictive models using the multi-year records of individual plant growth, survival and recruitment in the (20) original permanent plots from 19XX to 19XX.   Each estimated the effects of temperature, precipitation and soil moisture on

@@

### Changes in climate and community composition
